---
title: "psaverse"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{psaverse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(psaverse)
```

## Setting up a PSA Project Package

First, you would need to run the `psa_create_project()` function including the path you want to start the folder on your computer and the name of the project. After you run this function, the new package R project will open automatically for you.  

```{r eval = F}
psa_create_project(
  path = "~/Github", # path you want this on your computer
  psa_name = "PSA007-SPAML" # name of the project 
)
```

## Create/Update Descriptions

You can update the description of the package using the `psa_update_description()` function. 

```{r eval = F}
psa_update_description(
    package_title = NULL,
    description = NULL,
    version = NULL,
    license = NULL
)
```

## Add Dataset

```{r eval = F}
psa_data(
)
```

## Add R Package Dependencies

After you add your R scripts in `.R` or `.Rmd` format, you can use a convenience function to add all libraries that can be found in those scripts. The default is to examine all files in the `inst` folder and add those packages.  

```{r eval = F}
psa_dependencies(
    scan_folder = "inst",
    add_package = NULL # has to be one at a time
    )
```

## Add R Package to PSA GitHub

First, you should confirm you have the ability to push to the PsySciAcc github organization at https://github.com/psysciacc. Please ask to be added to the team. 

Second, you can use the `psa_git()` function to initialize your new project as a github repository associated with the PsySciAcc organization. You can then use your favorite way to github to push and pull to update the package. The default is to create a private repository until you are ready to release the project. 

```{r eval = F}
psa_git()
```
