---
title: "psaverse"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{psaverse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(psaverse)
```

## Setting up a PSA Project Package

First, you would need to run the `psa_create_project()` function including the path you want to start the folder on your computer and the name of the project. After you run this function, the new package *R* project will open automatically for you. Use that *R* project to complete the rest of the steps below to ensure files/folders go into the correct directories. 

```{r eval = F}
psa_create_project(
  path = "~/Github", # path you want this on your computer
  psa_name = "PSA007-spaml" # name of the project 
)
```

## Create/Update Descriptions

You can update the description of the package using the `psa_update_description()` function. Here are the license options:
  
  - MIT License: "MIT"
  - Apache License 2.0: "Apache"
  - GNU General Public License: "GPLv2" or "GPLv3"
  - GNU Affero General Public License, version 3: "AGPLv3"
  - GNU Lesser General Public License: "LGPLv2.1" or "LGPLv3"
  - Creative Commons CC0 Public Domain Dedication: "CC0"
  - Creative Commons Attribution 4.0 International: "CC-BY"
  - Proprietary license: "Proprietary"
  
Note: say yes when it asks if you want to overwrite the license! 

```{r eval = F}
psa_update_description(
  package_title = "SPAML IS GREAT",
  description = "Here's a serious description of the project.",
  version = "0.0.1",
  license = "GPLv3"
)
```

You can add authors to the package for other project monitors or the lead author of the paper. 

```{r eval = F}
psa_add_author(
   given = "Lucy",
   family = "van Pelt",
   ORCID_number = "LUCY-ORCID-ID"
   role = c("aut", "cre"),
   email = "lucy@example.com")
```

## Create Folder Structure

`psa_create_folder("all")` will create the entire folder structure for the package, while you can also add one at a time. 

Other options: 

- "ethics": creates the "01_Ethics" folder.
- "power": creates the "02_Power" folder.
- "materials": creates the "03_Materials" folder.
- "procedure": creates the "04_Procedure" folder.
- "data": creates the "05_Data" folder.
- "analysis": creates the "06_Analysis" folder.
- "communication": creates the "07_Communication folder.
- "all": creates all eight main folders.
- Any other parameter option will be added into the 08_Other folder.

```{r eval = F}
# will create all folders 
psa_create_folder("all")

psa_create_folder("cheese")

# make sure this works in markdown as well as regular script 
```

## Add Documents

You can then manually move the files you need into the folder structure or use the `psa_add_documents()` function to add individual files or entire folders. 

```{r eval = F}
psa_add_documents(
  folder = "ethics", # where should it go
  path = "~/Downloads", # to a single file or directory
  should_replace = FALSE, # overwrite existing files?
  recursive = FALSE # better explain this in docs 
)

# recheck copying individual files 
# path should allow vector of file paths like a list of PDFs
# or a directory 
# or single file 
```

## Add R Package Dependencies

After you add your R scripts in `.R` or `.Rmd` format, you can use a convenience function to add all libraries that can be found in those scripts. The default is to examine all files in the `inst` folder and add those packages.  

```{r eval = F}
psa_dependencies(
    scan_folder = "inst",
    add_package = NULL # has to be one at a time
    )

# add qmd files 
# allow for vector of packages to be added 
```

## Add this Package to PSA GitHub

First, you should confirm you have the ability to push to the PsySciAcc github organization at https://github.com/psysciacc. Please ask to be added to the team. 

Second, you can use the `psa_git()` function to initialize your new project as a github repository associated with the PsySciAcc organization. You can then use your favorite way to github to push and pull to update the package. The default is to create a private repository until you are ready to release the project. 

```{r eval = F}
psa_git()
```

## Check Package Folders

This function will check that you meet the minimum requires for documentation and files for the PSA folder structure. You will receive information on what you are missing. 

Options: "ethics", "power", "materials", "procedure", "data", "analysis", "communication", "all". 

```{r eval = F}
psa_check_folder(folder = "ethics")

# be sure to set working directory to the project so make it a global function 
```

working folder should not be empty if so make it "."

can't write the testthat (or subfolders) for CRAN, so make sure it's writing to a temp directory
(check scienceverse)

https://scienceverse.github.io/scienceverse/index.html
https://github.com/scienceverse/scienceverse/

https://github.com/debruine/booktem/blob/master/tests/testthat/test-create_book.R
- preclean up
- and then if stops be sure to clean up as well 
